Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-07 journal paper/content/sec-intro.tex
Full draft for the "theory section".
Added a footnote re discrepancy for HardMax.

\begin{itemize}
\item We compare \HardMax and \HardMaxRandom decision rules. We find that the greedy algorithm often wins under \HardMax, with a strong evidence of the ``death spiral" effect mentioned earlier. As predicted by the theory, better algorithms prevail if the expected number of ``random" users is sufficiently large. However, this effect is negligible for smaller parameter values.

@@

\newpage
\section{STUFF FROM THE PREVIOUS VERSION}

>>>>

\begin{itemize}
\item We compare \HardMax and \HardMaxRandom decision rules. We find that the greedy algorithm often wins under \HardMax, with a strong evidence of the ``death spiral" effect mentioned earlier.%
\footnote{The greedy algorithm wins often but not always, whereas it
always wins under \TheoryModel. The reason for this discrepancy is that the greedy algorithm in the theoretical results is aware of the Bayesian prior.
}
 As predicted by the theory, better algorithms prevail if the expected number of ``random" users is sufficiently large. However, this effect is negligible for smaller parameter values.

@@

\newpage
\section*{STUFF FROM THE PREVIOUS VERSION}
